Self Regulation Ontology Retest Data Report

### 2017-04-28 SRO_Report.Rmd
added bootstrapped results

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("Spearman at t1")+
  ylab("Spearman at t2"))
```

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC at t1")+
  ylab("ICC at t2"))
```

------------------------------------------------------------------------
Bootstrapping

```{r eval=FALSE}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  if('icc' %in% metric){
    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('spearman' %in% metric){
    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('eta_sq' %in% metric){
    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('sem' %in% metric){
    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  return(out_df)
}
```

Bootstrapping everything at once in this way locally would take around four hours.
```{r eval=FALSE}
non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]

@@

>>>>

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(spearman.x, spearman.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("Spearman with transformation")+
  ylab("Spearman witouth transformation"))
```

```{r}
ggplotly(rel_df %>%
  mutate(dv = gsub(".logTr", "", dv)) %>%
  mutate(dv = gsub(".Re", "", dv)) %>%
  left_join(raw_rel_df, by = 'dv') %>%
  ggplot(aes(icc.x, icc.y, color = task.x, label=dv))+
  geom_point()+
  geom_abline(intercept = 0, slope=1)+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC with transformation")+
  ylab("ICC without transformation"))
```

## Bootstrapping

```{r eval=FALSE, echo=FALSE}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  if('icc' %in% metric){
    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('spearman' %in% metric){
    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('eta_sq' %in% metric){
    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('sem' %in% metric){
    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  return(out_df)
}

# Bootstrapping everything at once in this way locally would take around four hours.
non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]

@@

Summarized bootstrapped reliabilities

```{r}
boot_df <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/bootstrap_merged.csv')

boot_df = boot_df %>%
  drop_na() %>%
  mutate(icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)))

boot_df %>%
  group_by(dv) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r fig.height=36}
 boot_df %>%
  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
  geom_boxplot()+
  geom_point(data = rel_df, aes(x=dv, y = icc, color = "yellow"))+
  theme_bw()+
  coord_flip()
```
